    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{\textbf{Abhay Patil}} % Your Name
\vspace{3.0mm}
\newcommand{\course}{Computer Science and Engineering(Data Science)} % Your Program
\newcommand{\roll}{RA2111056010029} % Your Roll No.
\newcommand{\phone}{7738703045} % Your Phone Number
\newcommand{\emaila}{abhayspatil16@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone}\\
  {Roll No.: \roll } & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  Bachelor of Technology & \href{https://github.com/patilabhay0616}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} \\  
  {SRM Institute of Science and Technology,KTR} & \href{https://www.linkedin.com/in/abhay-patil-2b2a29229/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering(Data Science)}{CGPA: 8.6}
      {SRM Institute of Science and Technology}{2021-25}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}
\vspace{1mm}
%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, HTML+CSS, Javascript} \\
     \vspace{1.0mm}
     \textbf{Machine Learning Libraries }{: LLM, Numpy, Pandas, CNN, TensorFlow, Scikit-learn, Matplotlib, Keras, PyTorch, NLP, LSTM, YOLO, Transfer Learning}\\ 
     \vspace{1.0mm}
     \textbf{Web Frameworks}{: Flask, DJango} \\
     \vspace{1.0mm}
     \textbf{Tools}{: PowerBI, Selenium, VScode, Git, Github, Excel } \\ 
     \vspace{1.0mm}
     \textbf{Big Data Tools}{: Apache, Hadoop, Spark} \\
     \vspace{1.0mm}
     \textbf{Cloud Computing}{: AWS S3, AWS Databricks, AWS Lambda, AWS EC2, AWS IAM, AWS SageMaker, AWS Data Pipeline, AWS DynamoDB, AWS VPC} \\  
     \vspace{1.0mm}
     \textbf{Relevent Coursework}{: Machine Learning, Deep Learning, Data Structures \& Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering. } \\ 
     \vspace{1.0mm}
     \textbf{Areas of Interest}{: Data Science, Data Analyst, Machine Learning, Data Engineer, Business Analyst, Backend Developer.} \\
     \vspace{1.0mm}
    }}
 \end{itemize}
 \vspace{-16pt}
% Experience 
\vspace{1.5mm}
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Science Intern}{Online}
      {Restaurant For Future (ROF) }{Apr 2024 - July 2024}
      
      \vspace{-1.5mm}
      \resumeItemListStart
    \item {Building a chatbot for customer service in restaurants.}
    \item {Provides services like table management}
    \item {Revolutionize the dining experience with our user-friendly online table booking platform}
   
    \resumeItemListEnd
    \vspace{-3.0mm}
    \resumeSubheading
      {AWS Cloud Virtual Internship}{Online}
      {AICTE-Eduskills}{March 2024- May 2024}
      \vspace{1.0mm}
      \resumeItemListStart
      \vspace{-1.5mm}
    \item {In-depth understanding of AWS cloud computing services, including EC2, S3, RDS, Lambda, IAM, VPC, and more.}
    \item {Proficient in designing, deploying, and managing fault-tolerant, highly available, and scalable AWS solutions.}
    \item {Strong knowledge of architectural best practices, such as AWS Well-Architected Framework, security, performance, and cost optimization.}
    \item {Hands-on experience in cloud infrastructure provisioning, monitoring, and automation using AWS Management Console and AWS CLI.}
    \resumeItemListEnd
    
    \vspace{-2.5mm}
    
    \resumeSubheading
      {AWS AI/ML Virtual Internship}{Online}
      {AICTE-Eduskills}{Jan 2024 - March 2024}
      \vspace{1.0mm}
      \resumeItemListStart
\vspace{-1.5mm}
      
    \item {Designed and implemented machine learning models using Python and libraries such as TensorFlow, Keras, and Scikitlearn to solve business problems like predicting customer churn and sales forecasting.}
   
    \resumeItemListEnd
%
%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}

    \resumeProject
      {Chicken Disease Classification Using MLOPS and DVC Pipeline With Deployments On AWS} %Project Name
      {Machine Learning, Python, DVC, CI/CD Pipeline} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Developed and deployed a Chicken Disease Classification model using Machine Learning Operations (MLOps) practices.}
        \vspace{1mm}
        \item {Utilized DVC (Data Version Control) for efficient dataset versioning and experiment tracking.}
         \vspace{1mm}
        \item {Implemented CI/CD pipelines for seamless model training, testing, and deployment.}
        \vspace{1mm}
        \item {Automated model updates and monitoring to ensure high accuracy and performance in production.
        \vspace{1mm}
        \item {Deployed the classification model on AWS using services like S3, EC2, and Lambda for scalable and cost-effective solutions.}
}
    \resumeItemListEnd
     \resumeProject
      {News Research Tool} %Project Name
      {Used Python, Langchain, Streamlit, OpenAI API, FAISS.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Load URLs or upload text files containing URLs to fetch article content.}
        \vspace{1mm}
        \item {Process article content through LangChain's UnstructuredURL Loader.}
        \vspace{1mm}
        \item {User-friendly news research tool designed for effortless information retrieval.}
    
      \resumeItemListEnd
    \vspace{-1mm}
    
    \resumeProject
      {Call centre Dashboard} %Project Name
      {Used PowerBI } %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {The dashboard uncovers long term trends in customer and agent behavior which will serve as basis for discussion with management}
      
        \item {The aim of the project was to create a dashboard in Power BI for Call Centre Manager that reflects all relevant Key Performance Indicators (KPIs) and metrics in the dataset.}
    \resumeItemListEnd
    \vspace{2mm}

    \resumeProject
      {Chatbot for online food ordering system} %Project Name
      {Used Python, NLP, Google Dialogflow.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Designed to enhance user experience, the chatbot seamlessly interprets and responds to user queries,streamlining the ordering process.}
        \vspace{1mm}
        \item {Build a chatbot for food orders online delivery using Google's Dialogflow ES.}
    \resumeItemListEnd

    \resumeProject
      {AWS, Databricks, Spark for Data Engineers} %Project Name
      {Machine Learning, Python, DVC, CI/CD Pipeline} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Conducted comprehensive IPL data analysis using AWS, Databricks, and Apache Spark to derive actionable insights from large datasets.}
        \vspace{1mm}
        \item {Leveraged AWS services like S3 for data storage, EMR for scalable processing, and Redshift for data warehousing.}
        \vspace{-2.5mm}
        \item {Utilized Databricks for managing Spark clusters, enabling efficient data processing, and collaborative notebook development.}
        \vspace{1.5mm}
        \item {Implemented ETL pipelines using Apache Spark to clean, transform, and aggregate IPL data, ensuring data quality and consistency.}
        \vspace{1.5mm}
        \item {Visualized key insights using Databricks’ integrated visualization tools and external BI tools, providing stakeholders with interactive and insightful dashboards.}

    \resumeItemListEnd


      
  \resumeSubHeadingListEnd
\section{\textbf{Certifications}}
  \vspace{2.0mm}

  AWS Academy Machine Learning Foundations (AWS) & \href{https://www.credly.com/earner/earned/badge/eb7380b5-b202-4c7e-893b-73bd1d1c6997}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
   AWS Academy Cloud Foundations (AWS) & \href{https://www.credly.com/earner/earned/badge/69763068-d925-4e4b-9b53-2e2bd8969cfb}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
   Introduction to Generative AI (Google) & \href{https://www.cloudskillsboost.google/public_profiles/55c03372-ed1f-487a-b9b0-febd62ca66d8/badges/7154476?utm_medium=social&utm_source=linkedin&utm_campaign=ql-social-share}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
    Complete A.I. & Machine Learning, Data Science Bootcamp (Udemy) & \href{https://www.udemy.com/certificate/UC-3009bcdf-10f2-47ba-af5f-f6db22f4460f/}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
   Big Data Foundation (IBM)  & \href{https://www.credly.com/earner/earned/share/90230269-c34a-4388-95d8-ccd7dbb994ac}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
   Hadoop Data Access (IBM) & \href{https://www.credly.com/earner/earned/badge/d5594f48-e27c-4d82-a705-353674c7d056}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\  
   \vspace{2.0mm}
   SQL and Relational Databases \href{https://courses.cognitiveclass.ai/certificates/993a2777e6d74027afc3a961d3ac9ffd}{\raisebox{0.0\height}{\footnotesize}\ {Link}} \\
   
\section{\textbf{Soft Skills and Position of Responsibilities}}
\vspace{1.5mm}
Leadership, Communication, Problem Solving, Analytical Thinking, Teamwork, Adaptability, Time Management, Creativity
\vspace{5.5mm}

Committee Head - Aarush, SRM University
\vspace{1.5mm}

Lead - Creatives Domain - SRM ASV
\vspace{-8.5mm}

\vspace{1.0mm}


    
    
    \vspace{1.0mm}
      

\vspace{-5.5mm}















% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}

